---
title: "allvignettes"
output: md_document
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
---

## Most expensive teams by average FPL player cost

Suppose we are interested in comparing which Premier League teams have the most expensive FPL players on average?

First we fetch the full summary data on all FPL players using the get_player_info function:

```{r, warning=F}

library(fplscrapR)

df <- get_player_info()
```

Next we use dplyr and ggplot2 to transform and plot the data, ranking each Premier League by its average FPL player cost:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  select(id, team, now_cost) %>% # selecting the relevant columns
  mutate(now_cost=now_cost/10) %>% # transforming the cost to millions (for some reason the FPL data structures FPL cost as 100.000s)
  group_by(team) %>% # transformation to group and mean-summarize the costs at the 'team' variable level 
  summarize(mean(now_cost)) %>%
    ggplot() + # plotting using ggplot2
    geom_col(aes(x=reorder(team,-`mean(now_cost)`),y=`mean(now_cost)`),fill="blue") +
    theme_bw() +
    scale_x_discrete(
      labels=c("1"="ARS","2"="BOU","3"="BHA","4"="BUR","5"="CAR","6"="CHE",
        "7"="CRY","8"="EVE","9"="FUL","10"="HUD","11"="LEI","12"="LIV",
        "13"="MCI","14"="MUN","15"="NEW","16"="SOU","17"="TOT","18"="WAT",
        "19"="WHU","20"="WOL")) +
    labs(x="Team",y="Mean player cost (£m)",
      title="Mean FPL player cost for Premier League teams",
      caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

***

## Comparing historical FPL total season scores for Eden Hazard and Alexis Sanchez

Suppose we are interested in how the FPL histories of Eden Hazard and Alexis Sanchez compare?

First we fetch the player histories of those two players using get_player_hist, mobilising their playerids using get_player_id:

```{r, warning=F}

library(fplscrapR)

df <- get_player_hist(playerid=get_player_id(c("Eden Hazard","Alexis Sánchez"))$id)
```

Next we use dplyr and ggplot2 to transform and plot the data, showing the total FPL scores by season for the two players across their FPL careers:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  select(playername,season_name,total_points) %>% # selecting the relevant columns
  ggplot() + # plotting using ggplot2
    geom_line(aes(x=season_name,y=total_points,group=playername,colour=playername),size=1) +
    theme_bw() +
    labs(x="Season",y="Total score",title="Historical FPL season scores by Hazard and Sanchez",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

***

## Aubameyang ownership and net transfers for the first 25 gameweeks"

Suppose we are interested in how the ownership of Pierre-Emerick Aubameyang has changed through transfers over the course of the first 25 gameweeks of the year?

First we fetch the gameweek-by-gameweek details of the player using get_player_details, mobilising the playerid using get_player_id:

```{r, warning=F}

library(fplscrapR)

df <- get_player_details(get_player_id("Pierre-Emerick Aubameyang")$id)
```

Next we use dplyr, tidyr and ggplot2 to transform and plot the data, showing the total number of owners and net transfers out for each gameweek:

```{r, message=F,warning=F}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  filter(round %in% 1:25) %>% # filtering for the GWs we are interested in
  select(round,transfers_balance,selected) %>% # selecting the relevant columns
  gather("var","value",-round) %>% # transforming from wide to long format for ggplot
  ggplot() + # plotting using ggplot2
    geom_line(aes(x=round,y=value,group=var,colour=var),size=1) +
    theme_bw() +
    scale_x_continuous(breaks=1:25) +
    labs(x="Gameweek",title="Aubameyang ownership and net transfers",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

***

## Mohamed Salah's points in each gameweek for the first 25 gameweeks

Suppose we are interested in the progression and variance of Mohamed Salah's FPL score in each gameweek? Here, we take the first 25 gameweeks of the season as an example.

First we fetch the gameweek-by-gameweek details of the player using get_player_details, mobilising the playerid using get_player_id:

```{r, warning=F}

library(fplscrapR)

df <- get_player_details(get_player_id("Mohamed Salah")$id)
```

Next we use dplyr and ggplot2 to transform and plot the data, showing Salah's round score for each gameweek:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  filter(round %in% 1:25) %>% # filtering for the GWs we are interested in
  select(round,total_points) %>% # selecting the relevant columns
  ggplot() + # plotting with ggplot2
    geom_col(aes(x=round,y=total_points),fill="red",size=1) +
    theme_bw() +
    scale_x_continuous(breaks=1:25) +
    labs(x="Gameweek",y="Round score",title="Salah's round score by gameweek",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

***

## List of top performers by FPL goals and assists

Suppose we are interested in listing the top FPL performers by FPL goals and assists? Again, we take the first 25 gameweeks of the season as an example.

First we fetch the gameweek-by-gameweek details of ALL players using get_player_details:

```{r, warning=F}

library(fplscrapR)

df <- get_player_details() # this may take a while to load as it fetches ALL player details
```

Next we use dplyr and ggplot2 to transform and plot the data, showing the top performers:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F}
df %>%
  filter(round %in% 1:25) %>% # filtering for the GWs we are interested in
  select(playername,goals_scored,assists) %>% # selecting the relevant columns
  group_by(playername) %>% # transformation to group and summarize the performance at the 'playername' variable level
  summarize_all(sum) %>% 
  mutate("involvements"=goals_scored+assists) %>% # adding a new variable that sums the goals scored and assists
  arrange(-involvements) %>%  # ordering (arranging) the table by top involvements
  slice(1:20) # showing the top20 only
```

***

## Building a very simple expected assists (xA) model

Suppose we are interested in trying to build an 'expected assists' (xA) model from the FPL data? Again, we take the first 25 gameweeks of the season as an example.

First we fetch the gameweek-by-gameweek details of ALL players using get_player_details, then create our model dataset by selected information that could predict assist performance, such as Key Passes and Open Play Crosses:

```{r, warning=F,message=F}

library(fplscrapR)
library(dplyr)

df <- get_player_details() # this may take a while to load as it fetches ALL player details

dfmodel <- df %>% 
  filter(round %in% 1:25) %>% # filtering out the rounds we are interested in
  mutate(potentialassists = key_passes+open_play_crosses) %>% # creating a new variable that give us a potential indicator for expected assists, namely the number of key passes and open play crosses for each player
  select(playername,assists,potentialassists) %>% # selecting the variables we need for our analysis
  group_by(playername) %>% # transformation to group and summarize all our variables (i.e. the actual and potential assists) at the 'playername' variable level
  summarize_all(sum) %>%
  mutate(xA=potentialassists*(sum(assists)/sum(potentialassists))) # creating a new variable called 'xA' that attempts to predict the actual number of assists based on the relationship (from our data) between the number of assists and key passes+open play cross a player has produced
```

Next we use dplyr and ggplot2 to transform and plot the data, comparing the actual FPL assists with our 'xA' model predictions. We also use the 'ggrepel' package to avoid cluttering of our plot:

```{r, message=F,warning=F}
library(ggplot2)
library(ggrepel)
```

```{r,warning=F,fig.width=7,fig.height=5}
dfmodel %>% 
  ggplot(aes(x=xA,y=assists)) +
  geom_point(alpha=0.5,size=2) +
  theme_bw() +
  labs(x="Expected assists",y="Actual assists",title="Expected vs. actual assists",subtitle="Season 2018/2019 - Gameweeks 1-25", caption=paste("Data from fplscrapR | ",Sys.Date(),sep="")) +
  geom_abline(intercept=0,slope=1,colour="grey",size=0.5) + 
  geom_text_repel(size=3.75,aes(
  label=ifelse(xA>quantile(xA,prob=1-1.5/100),as.character(playername),ifelse(assists>quantile(assists,prob=1-1.5/100),as.character(playername),"")))) + #
  scale_x_continuous(limits=c(0,12),breaks=0:12) +
  scale_y_continuous(limits=c(0,12),breaks=0:12)
```

Here we can see that there is a significant variation around our expected assists. Ryan Fraser's ouput is, for instance, well predicted. Raheem Sterling and Leroy Sanés are not - the model firmly under-estimates their assists. Meanwhile, the assists of players like Lucas Digne and Andros Townsend are far over-estimated. 

Finally, we test our xA model to see how it fares in explaining the variation of actual assists, using the summary function from R base:

```{r,warning=F}
summary(lm(dfmodel,formula=xA ~ assists))
```

***

## Creating an 'Alternative FDR' (aFDR) ranking of opponents by FPL points allowed

Suppose now we are interested in trying to create an alternative to FPL's "FDR" (Fixture Difficulty Ranking) based on actual FPL points allowed?  Again, we take the first 25 gameweeks of the season as an example.

First we fetch the gameweek-by-gameweek details of ALL players using get_player_details:

```{r, warning=F}

library(fplscrapR)

df <- get_player_details() # this may take a while to load as it fetches ALL player details
```

Next we use dplyr and ggplot2 to transform and plot the data, ranking the teams by FPL points allowed:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  filter(round %in% 1:25) %>% # filter out the gameweeks we are interested in
  group_by(opponent_team) %>% # transformation to group and summarize the total_points (scored by a given player in a given round) by the opponent ('opponent_team') variable level
  summarize(sum(total_points)) %>% 
  ggplot(aes(x=reorder(opponent_team,`sum(total_points)`),y=`sum(total_points)`,fill=factor(opponent_team))) + 
    geom_col(colour="black") +
    theme_bw() +
    coord_flip() +
    scale_x_discrete(labels=c("1"="ARS","2"="BOU","3"="BHA","4"="BUR","5"="CAR","6"="CHE","7"="CRY","8"="EVE","9"="FUL","10"="HUD","11"="LEI","12"="LIV","13"="MCI","14"="MUN","15"="NEW","16"="SOU","17"="TOT","18"="WAT","19"="WHU","20"="WOL")) + # here we transform the numbered team labels to the FPL short letter names
    labs(x="Team",y="Total FPL points allowed",title="Alternative FDR ranking - by total FPL points allowed",subtitle="Season 2018/2019 - Gameweeks 1-25",caption=paste("Data from fplscrapR | ",Sys.Date(),sep="")) +
    scale_fill_manual(values=c("1"="#EF0107","2"="#000000","3"="#0057B8","4"="#6C1D45","5"="#0070B5","6"="#034694","7"="#1B458F","8"="#003399","9"="#FFFFFF","10"="#0E63AD","11"="#003090","12"="#C8102E","13"="#6CABDD","14"="#DA291C","15"="#241F20","16"="#D71920","17"="#132257","18"="#FBEE23","19"="#7A263A","20"="#FDB913"),guide=F) # here we add the team-specific colours to the plot
```

***

## Creating a simple fixture table

Suppose now we are interested in creating a simple overview of FPL fixtures? Again, we take the first 25 gameweeks of the season as an example.

First we fetch the full fixture list using get_game_list:

```{r, warning=F}

library(fplscrapR)

gamelist <- get_game_list()
```

FPL only lists the fixtures once, as HOME-AWAY, but we need both HOME-AWAY and AWAY-HOME to plot the full fixture table. We need to plot every fixture twice, once as a home game for the one team, and once as an away game for the other team.

Using R base's rbind and dplyr's mutate (creating new variables) we essentially just duplicate the fixture table:

```{r, message=F,warning=F}
library(dplyr)
```

```{r, warning=F}

allfixtures <- rbind(
  gamelist %>% mutate(team=home,oppo=away,homeaway="home"),
  gamelist %>% mutate(team=away,oppo=tolower(home),homeaway="away"))
```

Next we use dplyr and ggplot2 to transform and plot the data, ranking the teams by FPL points allowed:

```{r,warning=F,fig.width=7,fig.height=5}
library(ggplot2)

allfixtures %>% 
  filter(GW %in% 1:25) %>% # filtering for the gameweeks we are interested in
    ggplot() +
      geom_tile(aes(x=GW,y=team),fill="white",colour="lightgrey") +
      geom_text(aes(x=GW,y=team,label=oppo),size=2) +
      theme_void() +
      theme(axis.text = element_text(face = "bold")) +
      theme(axis.text.y = element_text(margin=margin(0,-20,0,0))) + # fixing the margins on the tile
      scale_x_continuous(position="top",breaks=1:25) +
      labs(caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

***

## Creating an 'Alternative FDR' (aFDR) fixture table

Suppose now we are interested in creating an FPL fixture table that ranks fixtures by the 'Alternative FDR' (aFDR) metric? Again, we take the first 25 gameweeks of the season as an example.

First we create the aFDR rankings table, by fetching the gameweek-by-gameweek details of ALL players using get_player_details, and then transforming that using dplyr:

```{r, warning=F}

library(fplscrapR)
library(dplyr)

df <- get_player_details() # this may take a while to load as it fetches ALL player details

afdrranks <- df %>% 
  filter(round %in% 1:25) %>% # filtering for the gameweeks we are interested in.
  group_by(opponent_team) %>% # transformation to group and summarize the total_points (scored by a given player in a given round) by the opponent ('opponent_team') variable level
  summarize(sum(total_points)) %>% 
  arrange(`sum(total_points)`) %>% # ordering (arranging) by total_points allowed
  mutate(oppo=recode(opponent_team,"1"="ARS","2"="BOU","3"="BHA","4"="BUR","5"="CAR","6"="CHE","7"="CRY","8"="EVE","9"="FUL","10"="HUD","11"="LEI","12"="LIV","13"="MCI","14"="MUN","15"="NEW","16"="SOU","17"="TOT","18"="WAT","19"="WHU","20"="WOL")) # here we transform the numbered team labels to the FPL short letter names
```

Next, we fetch the full fixture list using get_game_list:

```{r, warning=F}

gamelist <- get_game_list()

```

FPL only lists the fixtures once, as HOME-AWAY, but we need both HOME-AWAY and AWAY-HOME to plot the full fixture table. We need to plot every fixture twice, once as a home game for the one team, and once as an away game for the other team.

Using R base's rbind and dplyr's mutate (creating new variables) we essentially just duplicate the fixture table:

```{r, warning=F}
afdrfixtures <- rbind(
  gamelist %>% mutate(team=home,oppo=away,homeaway="home"),
  gamelist %>% mutate(team=away,oppo=tolower(home),homeaway="away"))
```

Then we need to add in the aFDR ranking for each fixture, doing so through a loop (which is decidedly not the most efficient method). For each row, we identify the data point in the afdrranks data frame that provides the aFDR ranking for each team in question:

```{r, warning=F}
for (i in 1:nrow(afdrfixtures)){
  afdrfixtures$afdr[i] <- afdrranks$`sum(total_points)`[which(afdrranks$oppo==toupper(afdrfixtures$oppo[i]))]
}
```

Next we use dplyr and ggplot2 to plot the data in a fixture table:

```{r,warning=F,fig.width=7,fig.height=5}

library(ggplot2)

afdrfixtures %>% 
  filter(GW %in% 1:25) %>% # filtering for the gameweeks we are interested in 
  ggplot() +
    geom_tile(aes(x=GW,y=team,fill=afdr),colour="lightgrey") +
    geom_text(aes(x=GW,y=team,label=oppo),size=2) +
    theme_void() +
    theme(axis.text = element_text(face = "bold")) +
    theme(axis.text.y = element_text(margin=margin(0,-20,0,0))) + # fixing the margins
    scale_x_continuous(position="top",breaks=1:25) +
    labs(caption=paste("Data from fplscrapR | ",Sys.Date(),sep="")) +
    scale_fill_gradient2(guide=F,low="#00FF87",mid="#D6DCD8",high="#7F002D",midpoint=median(afdrfixtures$afdr)) # creating a gradient colour-coding that spans from lowest aFDR ranking (coloured red) to highest (coloured green)
```

***

## Creating your own 'FDR' fixture table

Suppose now we are interested in creating an FPL fixture table like the FPL's official 'Fixture Difficulty Ranking'? Again, we take the first 25 gameweeks of the season as an example.

First we fetch the official FDR rankings using get_fdr:

```{r, warning=F}

library(fplscrapR)

fdr <- get_fdr()
```

Next we fetch the full fixture list using get_game_list:

```{r, warning=F}

gamelist <- get_game_list()
```

FPL only lists the fixtures once, as HOME-AWAY, but we need both HOME-AWAY and AWAY-HOME to plot the full fixture table. We need to plot every fixture twice, once as a home game for the one team, and once as an away game for the other team.

Using R base's rbind and dplyr's mutate (creating new variables) we essentially just duplicate the fixture table:

```{r, message=F,warning=F}
library(dplyr)
```

```{r, warning=F}

fdrfixtures <- rbind(
  gamelist %>% mutate(team=home,oppo=away,homeaway="home"),
  gamelist %>% mutate(team=away,oppo=tolower(home),homeaway="away"))
```

Then we need to add in the FDR ranking for each fixture, doing so through a loop (which is decidedly not the most efficient method). For each row, we identify the data point in the fdr data frame that provides the FDR ranking for each team in question, depending on whether the fixture is home or away:

```{r, warning=F}
for (i in 1:nrow(fdrfixtures)){
  ifelse(fdrfixtures$homeaway[i]=="home",
    fdrfixtures$fdr[i] <- fdr$strength_overall_away[which(fdr$short_name==toupper(fdrfixtures$oppo[i]))],
    fdrfixtures$fdr[i] <- fdr$strength_overall_home[which(fdr$short_name==toupper(fdrfixtures$oppo[i]))])
}
```

Next we use dplyr and ggplot2 to plot the data in a fixture table:

```{r,warning=F,fig.width=7,fig.height=5}

library(ggplot2)

fdrfixtures %>% 
  filter(GW %in% 1:25) %>%  # filtering for the gameweeks we are interested in
    ggplot() +
      geom_tile(aes(x=GW,y=team,fill=fdr),colour="lightgrey") +
      geom_text(aes(x=GW,y=team,label=oppo),size=2) +
      theme_void() +
      theme(axis.text = element_text(face = "bold")) +
      theme(axis.text.y = element_text(margin=margin(0,-20,0,0))) + # fixing the margins
      scale_x_continuous(position="top",breaks=1:25) +
      labs(caption=paste("Data from fplscrapR | ",Sys.Date(),sep="")) +
      scale_fill_gradient2(guide=F,low="#00FF87",mid="#D6DCD8",high="#7F002D",midpoint=median(fdrfixtures$fdr)) # creating a gradient colour-coding that spans from toughest FDR ranking (coloured red) to easiest (coloured green)
```

***

## Finding the names of goalscorers in a given fixture

Suppose now we are interested in finding the names of the goalscorers in a given game? Here we take the example of the fixture West Ham - Crystal Palace.

First we find the gameid using get_game_list and dplyr:

```{r, warning=F}

library(fplscrapR)
library(dplyr)

gameid <- get_game_list() %>% filter(home=="WHU",away=="CRY") %>% select(id)

```

Next we fetch the game stats using get_game_stats:

```{r, warning=F}

df <- get_game_stats(gameid=gameid)
```

Next we identify the goalscorers' playerids:

```{r, warning=F}

goalscorerids <- unlist(list(df$goals_scored$a[[1]]$element,df$goals_scored$h[[1]]$element))
```

Finally we fetch the playernames of goalscorers using get_player_name:

```{r, warning=F}

get_player_name(playerid=goalscorerids)
```

***

## List your classic mini-leagues and current ranks

Suppose now we are interested in listing the classic mini-leagues of which you are a member and your current rank in those mini-leagues?

First we fetch the entry information using get_entry:

```{r, warning=F}

library(fplscrapR)

df <- get_entry(entryid=1076)

```

Next we select the classic league details and the relevant data columns using dplyr:

```{r, warning=F}

library(dplyr)

df$leagues$classic %>% 
  select(name,entry_last_rank) # selecting the columns of interest here

```

***

## Visualizing the FPL histories of entries

Suppose now we are interested in visualizing the FPL history of select entries, e.g myself (current FPL ID: 1076) and an FPL legend such as James Eggersdorff (current FPL ID: 64342)?

First we fetch the entry histories using get_entry_hist:

```{r, warning=F}

library(fplscrapR)

entryhist <- get_entry_hist(entryid=c(1076,64342))

```

Next we plot the historical performance using dplyr and ggplot2:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r, warning=F,fig.width=7,fig.height=5}
entryhist %>% 
  ggplot() +
  geom_line(aes(x=season_name,y=rank,group=name,colour=name)) +
  theme_bw() +
  theme(legend.position="top") +
  labs(x="Season",y="Overall Rank",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))

```

***

## Visualizing your in-season Overall Rank progress

Suppose now we are interested in visualizing the rank progression within the current season of our own FPL teams?

First I fetch my own entry season using get_entry_season:

```{r, warning=F}

library(fplscrapR)

myseason <- get_entry_season(entryid=1076)
```

Next we plot the historical performance using dplyr and ggplot2:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r, warning=F,fig.width=7,fig.height=5}
myseason %>% 
  ggplot() +
  geom_line(aes(x=event,y=overall_rank,group=name)) +
  theme_bw() +
  labs(x="Gameweek",y="Overall Rank",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))

```

***

## Listing the top 20 of your favourite mini-league

Suppose now we are interested in listing the top20 teams in your favourite mini-league? Here we take the example of the current 'Who Got the Assist? Mini-League'.

First we fetch the league data using get_league:

```{r, warning=F}

library(fplscrapR)

df <- get_league(leagueid = 441,leaguetype = "classic")
```

Next we show the top20 ranking teams at the moment using dplyr:

```{r, message=F,warning=F}
library(dplyr)
```

```{r, warning=F}
df$standings$results %>% # selecting the standings and results data
  select(entry,entry_name,player_name,rank,total) %>% # selecting the columns we are interested in displaying
  filter(rank %in% 1:20) # filtering for the top20 ranks

```

***

## Finding the most owned players amongst the top 20 teams of your favourite mini-league

Suppose now we are interested in finding the most owned players in the top20 teams in your favourite mini-league? Here we take the example of the current 'Who Got the Assist? Mini-League'.

First we fetch the league data using get_league:

```{r, warning=F}

library(fplscrapR)

df <- get_league(leagueid = 441,leaguetype = "classic")
```

Next we save in a new data frame the entry ids' of the top20 ranking teams at the moment, using dplyr:

```{r, message=F,warning=F}
library(dplyr)
library(tidyr)
```

```{r, warning=F}
top20entries <- df$standings$results %>% # selecting the standings and results data
  filter(rank %in% 1:20) %>%  # filtering for the top20 ranks
  select(entry) # selecting only the entry ids
```

Now we want to know the most selected players by these teams in a given gameweek, say gameweek 31. So we set the gameweek number and collect the players picks by each of the top20 entries using get_entry_picks. We do so through a loop (which is decidedly not the most efficient method), binding the picks together in a new data frame called 'top20picks':

```{r, warning=F}

gameweek <- 31

top20picks <- data.frame()

for (i in 1:nrow(top20entries)){
  picks <- get_entry_picks(entryid=top20entries[i,],gw=gameweek)
  top20picks <- rbind(top20picks,picks$picks)
}
```

Finally we list the top20 most owned players amongst the top20 managers in the WGTA Mini-League using dplyr:

```{r, warning=F}

top20picks %>% # working with our newly created data.frame
  group_by(element) %>% # transformation to group and summarize the count (number of times a given player was selected) at the element (the player) variable level
  summarize(n()) %>%
  arrange(-`n()`) %>% # arranging by most selected
  slice(1:20) %>% # slicing so we just see the top20 selected players
  arrange(element) %>% # arranging by element id in order to allow us to mutate (create a new variable) the element ids into player names 
  mutate(name=lapply(element,get_player_name)) %>% # adding the playername data
  tidyr::unnest(name) %>% # unnesting the playername data via tidyr
  select(playername,`n()`) %>% # selecting the variables of interest for our final list
  arrange(-`n()`) # arranging by most selected again

```

***

## Comparing total team BPS scores for a given game

Suppose now we are interested in comparing the total BPS scores for each team in a given game? Here we take the example of Manchester United - Leicester from round 1, game id 6.

First we fetch the game stats using get_game_stats:

```{r, warning=F}

library(fplscrapR)

df <- get_game_stats(gameid=6)
```

Next we structure a coherent data frame of the two teams' total BPS points, using R base's rbind and dplyr:

```{r, warning=F}

library(dplyr)

rbind( # combining the two objects containing the home and away team's BPS points
  data.frame(df$bps$a[[10]],team="away"),
  data.frame(df$bps$h[[10]],team="home")) %>% 
  group_by(team) %>% # transformation to group and summarize the value (bps points scored by a given player in the game) at the team variable level
  summarize(sum(value))
```

***

## Average and top entry scores for the first 25 gameweeks

Suppose we are interested in tracking the average and top FPL scores by gameweek?

First we fetch the round information for a selection of gameweeks, say 1-25, using the get_round_info function:

```{r, warning=F}

library(fplscrapR)

df <- get_round_info(1:25)
```

Next we use dplyr, tidyr and ggplot2 to transform and plot the data, showing the average and top entry progression by gameweek:

```{r, message=F,warning=F}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  select(id,average_entry_score,highest_score) %>% # selecting the relevant columns
  gather("var","value",-id) %>% # transforming from wide to long format for ggplot
  ggplot() + # plotting using ggplot2
    geom_line(aes(x=id,y=value,colour=var),size=1) +
    theme_bw() +
    scale_x_continuous(breaks=1:25) +
    labs(x="Gameweek",y="Score",title="Average and top FPL entry scores by gameweek",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```

