---
title: "Finding the names of goalscorers in a given fixture"
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Suppose now we are interested in finding the names of the goalscorers in a given game? Here we take the example of the fixture West Ham - Crystal Palace.

First we find the gameid using get_game_list and dplyr:

```{r, warning=F}

library(fplscrapR)
library(dplyr)

gameid <- get_game_list() %>% filter(home=="WHU",away=="CRY") %>% select(id)

```

Next we fetch the game stats using get_game_stats:

```{r, warning=F}

df <- get_game_stats(gameid=gameid)
```

Next we identify the goalscorers' playerids:

```{r, warning=F}

goalscorerids <- unlist(list(df$goals_scored$a[[1]]$element,df$goals_scored$h[[1]]$element))
```

Finally we fetch the playernames of goalscorers using get_player_name:

```{r, warning=F}

get_player_name(playerid=goalscorerids)
```

