---
title: "Creating a simple fixture table"
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Suppose now we are interested in creating a simple overview of FPL fixtures? Again, we take the first 25 gameweeks of the season as an example.

First we fetch the full fixture list using get_game_list:

```{r, warning=F}

library(fplscrapR)

gamelist <- get_game_list()
```

FPL only lists the fixtures once, as HOME-AWAY, but we need both HOME-AWAY and AWAY-HOME to plot the full fixture table. We need to plot every fixture twice, once as a home game for the one team, and once as an away game for the other team.

Using R base's rbind and dplyr's mutate (creating new variables) we essentially just duplicate the fixture table:

```{r, message=F,warning=F}
library(dplyr)
```

```{r, warning=F}

allfixtures <- rbind(
  gamelist %>% mutate(team=home,oppo=away,homeaway="home"),
  gamelist %>% mutate(team=away,oppo=tolower(home),homeaway="away"))
```

Next we use dplyr and ggplot2 to transform and plot the data, ranking the teams by FPL points allowed:

```{r,warning=F,fig.width=7,fig.height=5}
library(ggplot2)

allfixtures %>% 
  filter(GW %in% 1:25) %>% # filtering for the gameweeks we are interested in
    ggplot() +
      geom_tile(aes(x=GW,y=team),fill="white",colour="lightgrey") +
      geom_text(aes(x=GW,y=team,label=oppo),size=2) +
      theme_void() +
      theme(axis.text = element_text(face = "bold")) +
      theme(axis.text.y = element_text(margin=margin(0,-20,0,0))) + # fixing the margins on the tile
      scale_x_continuous(position="top",breaks=1:25) +
      labs(caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```
