---
title: "Finding the most owned players amongst the top 20 teams of your favourite mini-league"
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Suppose now we are interested in finding the most owned players in the top20 teams in your favourite mini-league? Here we take the example of the current 'The FF Community Shield' mini-league.

First we fetch the league data using get_league:

```{r, warning=F}

library(fplscrapR)

df <- get_league(leagueid = 786,leaguetype = "classic")
```

Next we save in a new data frame the entry ids' of the top20 ranking teams at the moment, using dplyr:

```{r, message=F,warning=F}
library(dplyr)
library(tidyr)
```

```{r, warning=F}
top20entries <- df$standings$results %>% # selecting the standings and results data
  filter(rank %in% 1:20) %>%  # filtering for the top20 ranks
  select(entry) # selecting only the entry ids
```

Now we want to know the most selected players by these teams in a given gameweek, say gameweek 31. So we set the gameweek number and collect the players picks by each of the top20 entries using get_entry_picks. We do so through a loop (which is probably not the most efficient method), binding the picks together in a new data frame called 'top20picks':

```{r, warning=F}

gameweek <- 31

top20picks <- data.frame()

for (i in 1:nrow(top20entries)){
  picks <- get_entry_picks(entryid=top20entries[i,],gw=gameweek)
  top20picks <- rbind(top20picks,picks$picks)
}
```

Finally we list the top20 most owned players amongst the top20 managers in the WGTA Mini-League using dplyr:

```{r, warning=F}

top20picks %>% # working with our newly created data.frame
  group_by(element) %>% # transformation to group and summarize the count (number of times a given player was selected) at the element (the player) variable level
  summarize(n()) %>%
  arrange(-`n()`) %>% # arranging by most selected
  slice(1:20) %>% # slicing so we just see the top20 selected players
  arrange(element) %>% # arranging by element id in order to allow us to mutate (create a new variable) the element ids into player names 
  mutate(name=lapply(element,get_player_name)) %>% # adding the playername data
  tidyr::unnest(name) %>% # unnesting the playername data via tidyr
  select(playername,`n()`) %>% # selecting the variables of interest for our final list
  arrange(-`n()`) # arranging by most selected again

```
