---
title: "My Expected Points"
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Suppose we are interested in how many points our team is expected to score in the next GW?

With fplscrapR, it's just a few lines of code away.

First, we fetch the player selection using get_entry_picks. Here I use the example of my own team for GW33. Since I used my Free Hit in 32, I have to fetch the team from GW31:

```{r, warning=F}

library(fplscrapR)

picks <- get_entry_picks(entryid=1076,gw=31)$picks
```

Next we fetch the Official FPL Expected Points projections using get_player_info() and select only what we need: the player id (renamed 'element' for merging later), the player name, and the expected points projection ('ep_next'), which we indicate is a numeric vector.

```{r, message=F,warning=F}
library(dplyr)

df <- get_player_info() %>% 
  select(id,playername,ep_next) %>% 
  mutate("element"=id)

df$ep_next <- as.numeric(df$ep_next)

```

Finally we merge the two, select out the variables of interest, display the projections, and sum up the total expected points from our starting 11:

```{r, message=F,warning=F}

df2 <- left_join(picks,df,by="element") %>% select(playername,is_captain,is_vice_captain,ep_next)

df2

sum(df2$ep_next[1:11])
```
