---
title: "Mohamed Salah's points in each gameweek for the first 25 gameweeks"
author: "Rasmus Wiscostretford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Suppose we are interested in the progression and variance of Mohamed Salah's FPL score in each gameweek in '18/19? Here, we take the first 25 gameweeks of the season as an example.

First we fetch the gameweek-by-gameweek details of the player using get_player_details, mobilising the playerid using get_player_id:

```{r, warning=F}

library(fplscrapR)

df <- get_player_details(name="Mohamed Salah",season=18)
```

Next we use dplyr and ggplot2 to transform and plot the data, showing Salah's round score for each gameweek:

```{r, message=F,warning=F}
library(dplyr)
library(ggplot2)
```

```{r,warning=F,fig.width=7,fig.height=5}
df %>% 
  filter(round %in% 1:25) %>% # filtering for the GWs we are interested in
  select(round,total_points) %>% # selecting the relevant columns
  ggplot() + # plotting with ggplot2
    geom_col(aes(x=round,y=total_points),fill="red",size=1) +
    theme_bw() +
    scale_x_continuous(breaks=1:25) +
    labs(x="Gameweek",y="Round score",title="Salah's round score by gameweek",caption=paste("Data from fplscrapR | ",Sys.Date(),sep=""))
```
